Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-04 draft.tex
AKSZ

\begin{qtn}
Is the canonical map \eqref{eqn: can cen int} always a weak equivalence?
\end{qtn}

@@

\section{Universal bulk TFT}
\label{sec: TFT}

Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.

The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
manifold with boundary.

We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}. 
Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.

In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.

@@

@@

\brian{or there exists a filtration on the constructible factorization algebra whose associated graded is a commutative P0 constructible factorization algebra or $1$-shifted Poisson.}
\brian{as a corollary butson-yoo}
\brian{main thrust is to interpret this in terms of the BV / BD formalism}

\begin{thm}
Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
\begin{itemize}
\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
\end{itemize}
\end{thm}

@@

\subsection{The bulk TFT}

Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct.

\begin{dfn}
For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
\[
\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
\]
The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
\end{dfn}

We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory".

We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
Recall, this model is given by the factorization algebra on $M$:
\begin{equation}\label{eqn:centerTFT}
\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
\end{equation}

The ``dequantization" is defined using the following filtration of this model.
For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space.

\begin{dfn}
Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
\end{dfn}

This is a filtration of factorization algebras on $M$. 
The associated graded factorization algebra is
\[
{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
\]
Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains.

 \begin{lmm}
There is a quasi-isomorphism of commutative factorization algebras on $M$:
\[
\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
\end{lmm}

@@

>>>>

\begin{qtn}
Is the canonical map \eqref{eqn: can cen int} a weak equivalence when $\UU_n \fg$ is replaced by an arbitrary $E_n$-algebra?
\end{qtn}

@@

\section{Universal bulk TFT}
\label{sec: TFT}
%
%Given an $E_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
%This is obtained by ``forgetting" the $E_{n+1}$-algebra to an $E_1$-algebra then considering the left-modules for this $E_1$-algebra.
%
%The $E_n$-center, or $E_n$-Hochschild cohomology, of an $E_n$-algebra $A$ is the {\em universal} $E_{n+1}$-algebra which acts on $A$. 
%In Section \ref{sec:swiss} below, we will recall an elegant operadic interpretation of this universal picture and interpret it in terms of {\em constructible factorization algebras}. 
%In the case of $E_n$-enveloping algebras, we will provide a strict factorization model of this universal situation in terms of a constructible factorization algebra on an $(n+1)$-dimensional 
%manifold with boundary. 
%
%We will furthermore provide an interpretation of this constructible factorization algebra in terms of the quantization of a certain topological field theory. 
%The key insight is that there is a {\em classical limit} of the $E_n$-center $\fZ_n(\fg)$ which is equivalent to the observables of an $(n+1)$-dimensional topological field theory known as {\em BF theory}. 
%Likewise, there is a classical limit of $\UU_n(\fg)$ which can be viewed as a boundary condition for BF theory.
%
%In this sense, topological BF theory is the universal $(n+1)$-dimensional field theory which has the $E_n$-enveloping algebra as a boundary condition. 
%This partially confirms the terminology used in \cite{ButsonYoo}  of topological BF theory as the ``universal bulk theory" of $\UU_n(\fg)$.

In this section, we turn to an interpretation of the $E_n$-center of an $E_n$-enveloping algebra in terms of a certain topological field theory (TFT).

@@

Abstractly, we know that any algebra over the Swiss cheese operad can be modeled as a constructible factorization algebra on a manifold with boundary. 
One drawback of the previous section is that we did not provide a model for the $E_n$-center of an enveloping algebra as a constructible factorization algebra on an $(n+1)$-dimensional manifold with boundary. 
There is, however, a certain ``dequantization" of the $E_n$-center that we do have an explicit description of.

The key insight is that there exists a filtration on our model for the $E_n$-center $\bZ_n(\fg)$ and the $E_n$-enveloping algebra $\bU_n (\fg)$ whose associated graded factorization algebras ${\rm Gr} \; \bZ_n(\fg)$ and ${\rm Gr} \; \bU_n(\fg)$ are {\em commutative} factorization algebras.

Our first main result is the following.

@@

\begin{prp}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible $\PP_0$-factorization algebra 
\begin{equation}\label{eqn:graded}
\left(\Tilde{\bZ}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
\end{equation}
on $M \times \RR_{\geq 0}$ such that $\pi_* \Tilde{\bZ}_n (\fg)$ is equivalent to ${\rm Gr} \; \bZ_n(\fg)$ as commutative factorization algebras on $M$ where $\pi : M \times \RR_{\geq 0} \to M$ is the projection. 
\end{prp}

A $\PP_0$, or $1$-shifted Poisson, algebra is a commutative dg algebra equipped with a bracket of cohomological degree $+1$ that satisfies a graded version of the Jacobi identity and is a biderivation with respect to the commutative product \brian{reference}. 
Likewise, a $\PP_0$-factorization algebra is a factorization algebra whose value on each open set is $\PP_0$-algebra.

The Batalin--Vilkovisky (BV) formalism for studying quantum field theory \brian{finish}

Following the proof of this proposition, our main thrust is to interpret this result in the BV formalism by exhibiting a topological field theory on the $(n+1)$-dimensional manifold with boundary $M \times \RR_{\geq 0}$ whose factorization algebra of classical observables is precisely the constructible factorization algebra in (\ref{eqn:graded}).

\brian{as a corollary butson-yoo}

%\begin{thm}
%Let $M$ be a smooth $n$-manifold and $\fg$ a Lie algebra. 
%There is a constructible factorization algebra on $M \times [0,1)$ satisfying the following properties:
%\begin{itemize}
%\item[(1)] On the $n$-dimensional stratum $M \times \{0\}$ the factorization algebra is equivalent to $\bU_n(\fg)$.
%\item[(2)] On the $(n+1)$-dimensional stratum $M \times (0,1)$, the factorization algebra is a quantization of the observables of topological BF theory based on the Lie algebra $\fg$.
%\item[(3)] Locally on $\RR^n \times [0,1)$ this factorization algebra produces \brian{deligne picture how to say}
%\end{itemize}
%\end{thm}

@@

\subsection{The bulk factorization algebra}

Let $M$ be an $n$-dimensional manifold and $\fg$ a Lie algebra.

\begin{dfn}
For an open set $U \subset M \times \RR_{>0}$ let $\Tilde{\bZ}_n(\fg) (U)$ be the cochain complex 
\[
\Tilde{\bZ}_n(\fg) (U) = \clie \bigg(\fg \otimes \Omega (U) \; , \; \Sym \left(\fg \otimes \Omega_c(U) [2] \right) \bigg) .
\]
The assignment $\Tilde{\bZ}_n(\fg) (U)$ defines a locally constant factorization algebra on $M \times \RR_{>0}$. 
\end{dfn}

On each open set $U$, the cochain complex $\Tilde{\bZ}_n(\fg) (U)$ is actually a commutative dg algebra. 
In fact, it has the structure of a $\PP_0$-algebra where the $1$-shifted bracket $\{\cdot, \cdot\}$ is defined as follows.

\begin{prp}
$\Tilde{\bZ}_n(\fg)$ has the structure of a $\PP_0$-factorization algebra on $M \times \RR_{>0}$. 
\end{prp}
\begin{proof}
Note that as an underlying graded vector space $\Tilde{\bZ}_n(\fg) (U)$ is of the form
\[
{\rm Sym} \left(\fg^* \otimes \Bar{\Omega}_c (U) [n-1] \right) \; \Hat{\otimes} \; {\rm Sym}  \left(\fg \otimes \Omega_c(U) [2] \right)  .
\]
Let $x^* \otimes \alpha$ denote an element of $\fg \otimes \Bar{\Omega}_c (U)$ and $y \otimes \beta$ denote an element of $\fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $(x^* \otimes \alpha) \otimes 1$ and $1 \otimes (y \otimes \beta)$ is defined by
\begin{align*}
\{(x^* \otimes \alpha) \otimes 1 , 1 \otimes (y \otimes \beta)\} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{(x^* \otimes \alpha) \otimes 1 , (x'^* \otimes \alpha') \otimes 1\} & = 0 \\
\{1 \otimes (y \otimes \beta) , 1 \otimes (y' \otimes \beta')\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

\subsection{The ``classical limit"}

For any dg Lie (in fact, $L_\infty$) algebra, the Chevalley--Eilenberg cochain complex computing Lie algebra homology admits a natural filtration whose associated graded has the structure of a commutative dg algebra.
If $\fh$ is a dg Lie algebra, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
The associated graded is the free symmetric algebra on $\fh[1]$ thought of as simply a cochain complex:
\[
{\rm Gr} \; \clieu (\fh) = {\rm Sym} (\fh [1])  .
\]
Here, the differential on the right-hand side is simply the underlying linear differential of $\fh$ (in terms of $L_\infty$ algebras, this is the $1$-ary operation $\ell_1$).

The Lie bracket on $\fh$ endows ${\rm Sym} (\fh [1])$ with the additional structure of a $\PP_0$-algebra. 
On linear elements this is simply the Lie bracket on $\fh$, and one extends to the full symmetric algebra by the graded Leibniz rule.

Consider our factorization model for the $E_n$-enveloping algebra $\bU_n(\fg) = \clieu (\fg \otimes \Omega_c)$. 
The filtration on Chevalley--Eilenberg chains equips $\bU_n(\fg)$ with a filtration as a factorization algebra. 
Furthermore, the resulting associated graded ${\rm Gr} \; \bU_n (\fg)$ has the natural structure of a $\PP_0$-factorization algebra.

There is a similar filtration on our model for the $E_n$-center $\bZ_n(\fg)$. 
Define
\[
F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
\]
It is immediate to check that this is a filtration of factorization algebras and that its associated graded has the structure of a $\PP_0$-factorization algebra.
In fact, we have the following result, which explains the relationship to the ``bulk" $(n+1)$-dimensional factorization algebra $\Tilde{\bZ}_n(\fg)$ we introduced in the last section.

 \begin{lmm}
Let $M$ be an $n$-dimensional manifold.
There is a quasi-isomorphism of  $\PP_0$-factorization algebras on $M$:
\[
\pi_* \Tilde{\bZ}_n(\fg) \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
\]
where $\pi : M \times \RR_{>0} \to M$ is the projection. 
\end{lmm}

@@

Since the universal action of $\bZ_n(\fg)$ on $\bU_n (\fg)$ is compatible with the above filtrations, we obtain the following constructible factorization algebra on $M \times \RR_{\geq 0}$.

\begin{dfn}\label{dfn:constructible1}
Let $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n(\fg))$ be the following constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$:
\begin{itemize}
\item to an open set $U \subset M \times \RR_{> 0}$, we assign the cochain complex $\Tilde{\bZ}_n (\fg)(U)$.
\item to an open set $U \subset M \times \RR_{\geq 0}$ with $U \cap (M \times \{0\}) \ne 0$ we assign the cochain complex ${\rm Gr} \;\bU_n(\fg)(U)$. 
\end{itemize}
\brian{not sure how much to say about structure maps}
\end{dfn}

\subsection{Bulk-boundary topological field theory}

It is the central theme of \cite{CG1, CG2} that the observables of a perturbative quantum field theory define the structure of a factorization algebra. 
In this setup, one first uses the Batalin--Vilkovisky (BV) formalism to define a perturbative classical field theory. 
The key ingredient in this formalism is a $(-1)$-shifted symplectic structure on the classical space of fields. 
The observables, or functions on the classical space of fields is then equipped with the structure of a $\PP_0$-factorization algebra.

More recently in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the classical BV formalism on manifolds with boundary. 
Let $N$ be such a manifold with boundary and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
The definition of a classical BV theory on $N$ amounts to prescribing the following data:
\begin{itemize}
\item[(1)]
an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
\item[(2)] 
a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
This is called a {\em boundary condition}.
\end{itemize}
From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as ``topological BF theory". 
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
In the BV formalism, the perturbative space of fields of BF theory on $N$ consists of
\[
(A, B) \in \Omega^{\bu} (N) \otimes \fg [1] \oplus \Omega^{\bu} (N) \otimes \fg^* [n-1] .
\]
When $N$ is compact, the classical moduli space underlying this field theory has an elegant description in terms of the AKSZ formalism. 
It can be interpreted as the following mapping stack 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Perturbative BF theory is obtained by taking the tangent space of the above mapping stack near at the trivial $G$-bundle.
Concretely, the classical moduli space consists of pairs $(A, B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d_A B + [A,B] & = 0 .
\end{align*}

Now, suppose $N$ has a boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

For BF theory, there is a natural choice of a Lagrangian for this boundary condition. 
In terms of mapping stacks, it is given by considering maps from $N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
\[
{\rm Map}(N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
\]
Then, by abstract maneuvers \brian{reference} the following fiber product
\[
\begin{tikzcd}
X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
\end{tikzcd}
\]
is equipped with a $(-1)$-shifted symplectic structure. 
Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.

Perturbatively, we follow \cite{ButsonYoo} and \cite{Eugene} to make the following definition within the BV formalism.

\begin{dfn}
Let $M$ be an $n$-dimensional manifold.
{\em Topological BF theory with its universal Neumann boundary condition} is the classical bulk-boundary theory on $M \times \RR_{\geq 0}$ described as follows:
\begin{itemize}
\item[(1)] 
The bulk theory is that of topological BF theory on $M \times \RR_{>0}$, where the space of fields is 
\[
\cE|_{M \times \RR_{>0}} = \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg [1] \oplus \Omega^{\bu} (M \times \RR_{>0}) \otimes \fg^* [n-2] .
\]
\item[(2)] 
The boundary condition is determined by the subspace of the fields on the boundary
\[
\Omega^{\bu} (M) \otimes \fg^* [n-2] \subset \cE|_{M \times \{0\}} .
\]
\end{itemize}
\end{dfn}

We obtain the following by a direct unpacking of the setup in \cite{Eugene}.

\begin{prp}
The constructible $\PP_0$-factorization algebra of topological BF theory with its universal Neumann boundary condition is equivalent to the constructible factorization algebra $(\Tilde{\bZ}_n (\fg), {\rm Gr} \bU_n (\fg))$ of Definition \ref{dfn:constructible1}. 
\end{prp}
%\subsection{The bulk TFT}
%
%Let us place the locally constant factorization algebra model of the $E_n$-enveloping algebra $\bU_n (\fg) = \clieu(\fg \otimes \Omega_c)$ on the $n$-manifold $M$.
%This factorization algebra is equivalent to the pushforward of a factorization algebra $\Obs_{\rm BF}$ on the $(n+1)$-dimensional manifold $M \times \RR$ along the projection $\pi : M \times (0,1) \to M$ which we proceed to construct. 
%
%\begin{dfn}
%For an open set $V \subset M \times (0,1)$ let $\Obs^{\rm cl}_{\rm BF} (V)$ be the cochain complex 
%\[
%\Obs^{\rm cl}_{\rm BF} (V) = \clie \bigg(\fg \otimes \Omega (V) \; , \; \Sym \left(\fg \otimes \Omega_c(V) [2] \right) \bigg) .
%\]
%The assignment $V \mapsto \Obs^{\rm cl}_{\rm BF}(V)$ defines a locally constant factorization algebra on $M \times (0,1)$. 
%\end{dfn}
%
%We note that $\Obs_{\rm BF}^{\rm cl}$ is a factorization algebra with values in commutative dg algebras. 
%In fact, it is given by the ``classical observables" of a topological field theory on $M \times (0,1)$ known as ``topological BF theory". 
%
%We now consider the pushforward factorization algebra $\pi_* \Obs^{\rm cl}_{\rm BF}$ on $M$.
%Locally, on disks, we will see that it is quasi-isomorphic to a certain limit, or ``dequantization", of our model for the $E_n$-center of $\UU_n \fg$.
%Recall, this model is given by the factorization algebra on $M$:
%\begin{equation}\label{eqn:centerTFT}
%\bZ_n(\fg) = \clie\left(\fg \otimes \Omega \, , \, \clieu (\fg \otimes \Omega_c) \right) .
%\end{equation}
%
%The ``dequantization" is defined using the following filtration of this model.
%For any Lie algebra $\fh$, let $\clieu_{\leq k} (\fh)$ be the subcomplex of Chevalley--Eilenberg chains which is $\Sym^{\leq k} (\fh[1])$ as an underlying graded vector space. 
%
%\begin{dfn}
%Introduce the filtration on the factorization algebra on $M$ in (\ref{eqn:centerTFT}) by 
%\[
%F^k \bZ_n(\fg) = \clie \bigg(\fg \otimes \Omega \; , \; \clieu_{\leq k} (\fg \otimes \Omega_c) \bigg) .
%\]
%\end{dfn}
%
%This is a filtration of factorization algebras on $M$. 
%The associated graded factorization algebra is
%\[
%{\rm Gr} \; \bZ_n(\fg) \; = \; \clie \bigg(\fg \otimes \Omega \; , \; \Sym \left(\fg \otimes \Omega_c [1] \right) \bigg) .
%\]
%Notice this is similar to the model $E_n$-center except we have turned off the Chevalley--Eilenberg differential on chains. 
%
% \begin{lmm}
%There is a quasi-isomorphism of commutative factorization algebras on $M$:
%\[
%\pi_* \Obs^{\rm cl}_{\rm BF} \; \xto{\simeq} \; {\rm Gr} \; \bZ_n(\fg) .
%\]
%\end{lmm}
%
%In fact, we will show that this quasi-isomorphism is a deformation retraction. 
%
%\begin{proof}
%To exhibit this quasi-isomorphism, we introduce the following cochain maps.
%For an open set $U \subset M$ let
%\[
%\int_\RR : \Omega_c(U \times \RR) \to \Omega_c (U) [1] 
%\] 
%be the map which integrates a compactly supported form on $U \times \RR$ along $\RR$. 
%This map is a quasi-isomorphism for any $U $ and admits the following explicit retract. 
%Let $\phi$ be a fixed compactly supported function on $\RR$ of mass $1$ and define
%\[
%r_\phi : \Omega_c(U) [1] \to \Omega_c (U \times \RR)
%\]
%by $r_\phi (\alpha) = \alpha \wedge \phi \, \d t$. 
%\end{proof}
